Holomorphic field theories and higher algebra

### 2024-09-20 draft.tex
tweaked BCOV subsection

%In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
Let $X$ be a complex threefold equipped with a Calabi--Yau structure; we denote by $\Omega \in \Omega^{3,hol}(X)$ the holomorphic volume form.
The primary field of Kodaira-Spencer theory is 
\beqn
\mu \in \Omega^{0,1}(X,\T_X),
\eeqn 
a $(0,1)$-form  on $X$ with values in the holomorphic tangent bundle~$\T_X$.
In contrast to examples above, a constraint is imposed on these sections:
we assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning 
\[
{\rm div}_\Omega(\mu) = 0,
\]
i.e., its divergence vanishes.
In short, the fields are divergence-free vector fields.
The equation of motion is 
\beqn
\dbar \mu + \frac12 [\mu,\mu]_{SN} = 0 ,
\eeqn
where $[-,-]_{SN}$ denotes here the Schouten--Nijenhuis bracket 
(which, on vector fields, is simply the Lie bracket, and is the natural multilinear extension to polyvector fields).
The reader might recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
Formulating the action functional to obtain this equation of motion is a little involved.

The action functional is similar to the Chern--Simons action:
\beqn\label{eqn:KS1}
S(\mu) = \int_X \left( \frac12 \mu\, \dbar \del^{-1} \mu + \frac13 \mu \wedge \mu \wedge \mu \right) .
\eeqn
\owen{Honestly I don't understand this formula. We need to unpack it more slowly in terms of explicit complex geometry.}
To make sense of this, 
note that $\Omega \in \Omega^{3,0}(X)$ and $\mu^3 \in \Omega^{0,3}(X, \cT^{\otimes 3})$.
In the integrand we use the Calabi--Yau form to obtain a $(3,3)$-form.
The integrand is not defined globally as it involves the distributional operator $\del^{-1}$.
Locally it is well-defined as any divergence-free vector field on affine space can be written as the divergence of a bivector field.
Nevertheless, this model can be carefully put into the rigorous framework of the Batalin--Vilkovisky formalism \cite{CLbcov1}.
Setting aside the apparent global issues, 
we apply formal variational calculus to this action to obtain the equation of motion.

>>>>

%In complex dimension $3$ there is a related theory, called Kodaira--Spencer theory, which only consists of the field $\mu$ describing the complex structure in the above example.
Let $X$ be a complex threefold equipped with a Calabi--Yau structure; we denote by $\Omega \in \Omega^{3,hol}(X)$ the holomorphic volume form.
The primary field of Kodaira-Spencer theory is 
\beqn
\mu \in \Omega^{0,1}(X,\T_X),
\eeqn 
a $(0,1)$-form  on $X$ with values in the holomorphic tangent bundle~$\T_X$.
In contrast to examples above, a constraint is imposed on these sections:
we assume that $\mu$ preserve the holomorphic volume form $\Omega$, meaning 
\[
{\rm div}_\Omega(\mu) = 0,
\]
i.e., its divergence vanishes.
In short, the fields are divergence-free vector fields.
The equation of motion is 
\beqn
\dbar \mu + \frac12 [\mu,\mu]_{SN} = 0 ,
\eeqn
where $[-,-]_{SN}$ denotes here the Schouten--Nijenhuis bracket 
(which, on vector fields, is simply the Lie bracket, and is the natural multilinear extension to polyvector fields).
The reader might recognize this equation as the Maurer--Cartan equation controlling deformations of complex structure $\dbar\rightsquigarrow \dbar + \mu$.
Formulating the action functional to obtain this equation of motion is a little involved, 
and we refer to \cite{CLbcov1} for a systematic discussion.

\begin{rmk}
The kinetic term has the form
\[
\int_X \frac12 \mu\, \dbar \del^{-1} \mu
\]
and hence resembles the chiral sector of the scalar, which we just discussed.
\end{rmk}
